Linking watershed nutrient loading to estuary water quality with semiparametric models

### 2023-06-23 Schramm-2023-06-PeerJ/Schramm-2023-06-PeerJ.Rmd
final formatting

# Acknowledgements
The author thanks Stephanie deVilleneuve for comments on an early draft and
members of the Coastal Nutrient Input Repository project committee for
supporting project development and their valuable input.

# Funding {.unnumbered}
This project was funded in part by a Texas Coastal Management Program grant 
approved by the Texas Land Commissioner, providing financial assistance under 
the Coastal Zone Management Act of 1972, as amended, awarded by the National 
Oceanic and Atmospheric Administration (NOAA), Office for Coastal Management,
pursuant to NOAA Award No. NA21NOS4190136. The views expressed herein are those 
of the author(s) and do not necessarily reflect the views of NOAA, the U.S. 
Department of Commerce, or any of their subagencies.

# Data Availability {.unnumbered}
Reproducible code and datasets generated during this study are available in
the Zenodo repository, https://doi.org/10.5281/zenodo.733075.

>>>>

# Acknowledgements {.unnumbered}
The author thanks Stephanie deVilleneuve for comments on an early draft and
members of the Coastal Nutrient Input Repository project committee for
supporting project development and their valuable input.

### 2023-06-23 Schramm-2023-06-PeerJ/Schramm-2023-06-PeerJ.tex
final formatting

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{funding}{%
\section*{Funding}\label{funding}}
\addcontentsline{toc}{section}{Funding}

This project was funded in part by a Texas Coastal Management Program
grant approved by the Texas Land Commissioner, providing financial
assistance under the Coastal Zone Management Act of 1972, as amended,
awarded by the National Oceanic and Atmospheric Administration (NOAA),
Office for Coastal Management, pursuant to NOAA Award
No.~NA21NOS4190136. The views expressed herein are those of the
author(s) and do not necessarily reflect the views of NOAA, the U.S.
Department of Commerce, or any of their subagencies.

\hypertarget{data-availability}{%
\section*{Data Availability}\label{data-availability}}
\addcontentsline{toc}{section}{Data Availability}

Reproducible code and datasets generated during this study are available
in the Zenodo repository, \url{https://doi.org/10.5281/zenodo.733075}.

>>>>

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

@@
